---
title: "Simple Predicting Conversion Rate from Data"
output:
  html_document: default
  pdf_document: default
---
## Load required libraries
```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```

## Read CSV Data and Cast Column Types
```{r cars}
conversion_data <- read_csv("conversion_data.csv",
                            col_types = cols(
                                             new_user = col_factor(levels = NULL),
                                             source = col_factor(levels = NULL),
                                             country = col_factor(levels = NULL)))
conversion_data

summary(conversion_data)

```

## Data Exploration

```{r}
#Histogram for Age
ggplot(conversion_data, aes(x=age)) + geom_histogram(binwidth = 5) + xlim(10,70)

#Histogram for Total Pages Visited
ggplot(conversion_data, aes(x=total_pages_visited)) + geom_histogram() 

```

```{r}
data_country_source <- conversion_data %>%                             
  group_by(country,source) %>%                                
  summarize(conversion_rate = mean(converted)) 

data_country_source

ggplot(data_country_source, aes(x=country, y=conversion_rate, fill = source))+  geom_col()

#country new users
data_country_users <- conversion_data %>%                             
  group_by(country,new_user) %>%                                
  summarize(conversion_rate = mean(converted)) 

data_country_users

ggplot(data_country_users, aes(x=country, y=conversion_rate, fill = new_user))+  geom_col()

#Single Value
data_country <- conversion_data %>%                             
  group_by(country) %>%                                
  summarize(conversion_rate = mean(converted)) 

data_country

ggplot(data_country, aes(x=country, y=conversion_rate, fill = country))+  geom_col()


data_source <- conversion_data %>%                             
  group_by(source) %>%                                
  summarize(conversion_rate = mean(converted)) 

data_source

ggplot(data_source, aes(x=source, y=conversion_rate, fill = source))+  geom_col()

data_age <- conversion_data %>%                             
  group_by(age) %>%                                
  summarize(conversion_rate = mean(converted)) 

data_age

ggplot(data_age, aes(x=age, y=conversion_rate))+  geom_line() + xlim(0,80) + scale_y_log10()

data_pages <- conversion_data %>%                             
  group_by(total_pages_visited) %>%                                
  summarize(conversion_rate = mean(converted)) 

data_pages

ggplot(data_pages, aes(x=total_pages_visited, y=conversion_rate))+  geom_line()

data_user <- conversion_data %>%                             
  group_by(new_user) %>%                                
  summarize(conversion_rate = mean(converted)) 

data_user

ggplot(data_user, aes(x=new_user, y=conversion_rate, fill = new_user))+  geom_col()
```
```{r}
pairs(conversion_data)
```

## Taking care of abnormal values
I see that some ages are impossible to achieve (eg. 123), therefore, we have to remove these values. I have decided to remove these observations.

```{r}
#Find the quantity of abnormal users
subset(conversion_data, age>79)

#filter them out
conversion_clean <- conversion_data %>%
  filter(age < 80)

conversion_clean
```

## Recode Categorical Variables for modelling

```{r}
conversion_wide <- conversion_clean %>%
  mutate(uk = recode(country, "UK" = 1,
                                .default = 0),
         usa = recode(country, "US" = 1,
                                .default = 0),
         china = recode(country, "China" = 1,
                                .default = 0),
         ads = recode(source, "Ads" = 1,
                                .default = 0),
         seo = recode(source, "Seo" = 1,
                                .default = 0)) %>%
  select(-country,-source)

conversion_wide

```


## Separate the data into training and testing sets

```{r}

## Train with 75% of the sample size
smp_size <- floor(0.75 * nrow(conversion_wide))

set.seed(123)

train_ind <- sample(seq_len(nrow(conversion_wide)), size = smp_size)

train <- conversion_wide[train_ind, ]
test <- conversion_wide[-train_ind, ]

train
test
```

## Logistic Regression
Because the response variable in this case (converted) is a categorical variable and the problem at hand is one of prediction, logistic regression is suitable for the matter.

```{r}
model <- glm(converted ~.,family=binomial(link='logit'),data=train)
summary(model)
anova(model, test="Chisq")
```

All of the variables have statistical significance. Therefore, we do not have to perform feature selection.


## Predicting Conversions and Model Accuracy

```{r}
fitted_results <- predict(model,test)

#Classifying the probabilities
fitted_results <- ifelse(fitted_results >= 0.5,1,0)

error <- mean(fitted_results != test$converted)
error

accuracy = 1 - error
accuracy

#Plot the confusion matrix
table(predicted = fitted_results,actual = test$converted)
```

## Final insights and recommendations

The company should consider increasing targeted marketing for younger users, users in Germany and existing users due to the higher conversion rate for these specific groups. 

People who are visiting a lot of pages also tend to have higher conversion rates. This is an indicator of intent to purchase. The company could also deploy targetted marketing strategies towards someone who has visited a lot of pages but has not made a purchase by sending them special offers on the products that have been viewed a lot by the customer. 

China is doing exceptionally poor with regards to conversion rate. There could be a problem with translation issues as all of the other factors (marketing source) are relatively equally spread amongst countries. Finding out why China is doing so poorly and fixing the issue that was previously unrecognised could potentially significantly improve conversion rate and company performance in China.

